Exercise 3: Software Architecture in Practice Case: Beer Web Store

### 2008-03-17 trunk/SAiP/Module1/H3/doc/architecturaldescription.tex
Architectural description updated.

\fixme{Skal vi tilføje applikationen til Web serveren? Den indeholder
ikke nogen aktive komponenter.}

@@

The benifits of a box-and-line drawing is that it can be written and "understood" by almost anyone, and in the initial phases of the architectual design they may be fine. They are fast to draw and can be shown to non-technical stakeholders. It is kind of like simple signlanguage - everyone understands nodding and shaking ones head or indicating a direction as long as it is for general information.

@@

Working as an developer/tester/engineer means that everything must be quantifiable in some way, and box-and-line drawings do not offer this unambigious quantifiability. For this a clearly defined modeling language, without ambiguaty as to the meaning of the model, is needed. An example of such a language is Unified Modelling Language(UML), which would allow the box-and-line drawing to be represented as one or more diagrams solving all the ambiguaty of the box-and-line drawing with only a single requirement; one must know the language, which is in deed one of the reasons while box-and-line drawings are still widely used - there is no single unambigious modelling language know by all stakeholders, and when that is the case it may be more confusing then benificial to spend time making sure the diagram is clear and unambigious, if that clarity is derived from symbolic notation that the readers (stakeholders) do not understand.

@@

As SOA consists of a collection of (preferrably stateless) well-defined services what needs to be desctibed is, which existing (external) services are needed and which new services has to be created. This may be done using the MacKenzie Topic maps, which describe the static dependencies between the services.

The static description is naturally not sufficient, and two other views may be presented to show the Dynamic interrelations; Visibility and Interaction.

\fixme{Finish question 2.4}

>>>>

The application code (Beer Web) and the database facade are
both deployed on the web server.

@@

The benifits of a box-and-line drawing is that it can be written and "understood" by almost anyone, and in the initial phases of the architectual design they may be fine. They are fast to draw and can be shown to non-technical stakeholders. It is kind of like simple sign-language - everyone understands nodding and shaking ones head or indicating a direction as long as it is for general information.

@@

Working as an developer/tester/engineer means that everything must be quantifiable in some way, and box-and-line drawings do not offer this unambigious quantifiability. For this a clearly defined modeling language, without ambiguity as to the meaning of the model, is needed. An example of such a language is Unified Modelling Language(UML), which would allow the box-and-line drawing to be represented as one or more diagrams solving all the ambiguaty of the box-and-line drawing with only a single requirement; one must know the language, which is indeed one of the reasons while box-and-line drawings are still widely used - there is no single unambigious modelling language known by all stakeholders, and when that is the case it may be more confusing then benificial to spend time making sure the diagram is clear and unambigious, if that clarity is derived from symbolic notation that the readers (stakeholders) do not understand.

@@

As SOA consists of a collection of (preferrably stateless) well-defined services what needs to be described is, which existing (external) services are needed and which new services has to be created. This may be done using the MacKenzie Topic maps, which describe the static dependencies between the services.

The static description is naturally not sufficient, and two other views may be presented to show the Dynamic interrelations for the services that are provided; Visibility and Interaction. The visibility view describes the awareness, willingness and reachability of a service and the interaction view describes how the service can be used (behaviour model) and the structure and semantics of the information that is provided (information model).
